---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidycensus)
library(acs) 
library(dplyr)
library(sf)
library(ggplot2)
library(ggthemes)
library(viridis)
library(scales)
library(naniar)
library(readr)

# variable list 
acs_variable_list <- load_variables(2017, "acs5", cache = TRUE)
# https://data.census.gov/cedsci/ 

census_api_key("5ff64f429a9814777a1756f1ab3665a07d46b6a5") # Brandon's Key
```

Chetty et al. (2014) identified five core factors correlated with economic mobility. Economic mobility is correlated with several neighborhood characteristics, including:

•	Segregation by race and poverty quantified by the fraction of non-Hispanic whites (~ -0.4); the fraction of individuals in poverty defined as the bottom income quartile (~ -0.5); and fraction of individuals who commute less than 15 minutes to work in a commuter zone (~ +0.6).
•	Quality of the K-12 school system quantified by output measures such income-adjusted test scores (~ +0.6) and high school graduation rate (~ +0.6); 
•	Social capital quantified by the social capital index, the index is comprised of voter turnout rates; the fraction of people who return their decennial census forms; and various measures of participation in community organizations (~ +0.6);
•	Family structure quantified by the fraction of children living in single-parent households (~ -0.7); the fraction of adults who are divorced (~ -0.5); and the fraction of adults who are married (~ +0.6);
•	Income inequality quantified by the Gini coefficient (~ -0.6); and the fraction of households in the middle class defined as the fraction of with incomes between the 1st and 3rd quartiles (~ +0.7).

We want to compare these factors in 2010 and 2018. 

```{r pull_acs_data, echo=FALSE}
tables <- c(
  "B01001", # age 
  "B02001",  # sex/gender and race/ethnicity 
  "B05010", # poverty status 
  "",
) 

# Get tables for counties --------------------------------------------------------------------------------------

# Iowa (FIPS 19)
dataia <- get_acs(geography = "county", state = 19, table = tables[1], year = 2018, survey = "acs5", 
                  cache_table = TRUE, output = "wide", geometry = TRUE, keep_geo_vars = TRUE)
for(i in 2:length(tables)){
  tmp <- get_acs(geography = "county", state = 19, table = tables[i],year = 2018, survey = "acs5", 
                 cache_table = TRUE, output = "wide", geometry = FALSE)
  dataia <- left_join(dataia, tmp)
}
remove(tmp)

# Oregon (FIPS 41)
dataor <- get_acs(geography = "county", state = 41, table = tables[1], year = 2018, survey = "acs5", 
                  cache_table = TRUE, output = "wide", geometry = TRUE, keep_geo_vars = TRUE)
for(i in 2:length(tables)){
  tmp <- get_acs(geography = "county", state = 41, table = tables[i],year = 2018, survey = "acs5", 
                 cache_table = TRUE, output = "wide", geometry = FALSE)
  dataor <- left_join(dataor, tmp)
}
remove(tmp)

# Virginia (FIPS 51)
datava <- get_acs(geography = "county", state = 51, table = tables[1], year = 2018, survey = "acs5", 
                  cache_table = TRUE, output = "wide", geometry = TRUE, keep_geo_vars = TRUE)
for(i in 2:length(tables)){
  tmp <- get_acs(geography = "county", state = 51, table = tables[i],year = 2018, survey = "acs5", 
                 cache_table = TRUE, output = "wide", geometry = FALSE)
  datava <- left_join(datava, tmp)
}
remove(tmp)

# Join
data <- rbind(dataia, dataor, datava)

data <- data %>% transmute(
  STATEFP = STATEFP, 
  COUNTYFP = COUNTYFP, 
  COUNTYNS = COUNTYNS, 
  AFFGEOID = AFFGEOID, 
  GEOID = GEOID, 
  LSAD = LSAD, 
  NAME.x = NAME.x, 
  NAME.y = NAME.y,
  NAME = NAME,
  ALAND = ALAND, 
  AWATER = AWATER, 
  geometry = geometry,
  # comment here 
  int_dialup = B28002_003E / B28002_001E * 100,
  
)
```














